
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{hussain-resume-openfont}
\usepackage{fancyhdr}
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome} % For social media icons
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Hussain}{Abbas}{ \\
\textcolor{red}{DELFT, NETHERLANDS}\\

\faPhone\ +393208186123 \ | \ \faEnvelope \ \href{mailto:hossainabbas747@gmail.com}{hossainabbas747@gmail.com} \ |  
\href{https://www.linkedin.com/in/hossaina007/}{\faLinkedin Linkedin} | \href{https://github.com/HossainA007}{\faGithub Github}| \href{https://www.youtube.com/@hossaina007}{\faYoutube YouTube} 
%| 
%\textcolor{blue}{VISA: Arbeid Vrij Toegestaan}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.63\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{University of St Cyril \& Methodius}
\descript{| CFD INTERN}
\location{Oct 2024 -  Dec 2024 | Skopje, North Macedonia}
\location{SUPERVISOR- Marija Lazarevijk}
\vspace{0.9em}
\begin{tightemize}
\justifying
\item Perform CFD analysis and modeling of unsteady, incompressible airflow around a wind turbine with varying inlet velocities using ANSYS FLUENT.
\end{tightemize}
\sectionsep

\runsubsection{CERN}
\descript{| MECHANICAL INTERN}
\location{Feb 2024 - JUN 2024 | Geneva, Switzerland}
\location{SUPERVISOR-Jan Buesa Orgaz}
\begin{tightemize}
     \justifying
     \item Conducted finite element (FE) thermo-mechanical simulations of beam impacts on mechanical components, including collimator jaws.
     \item Calculated forces on high-precision mechanical components using analytical methods.
\end{tightemize}
\sectionsep

\runsubsection{VOLVO CARS}
\descript{| THERMAL ANALYSIS TRAINEE}
\location{Feb 2023 - Feb 2024 | Gothenburg, Sweden}
\location{SUPERVISOR-RANDI FRANZSKE \& EMIL WILESON}
\begin{tightemize}
       \justifying 
        \item Optimized 3D CFD simulations of the VOLVO XC40 cabin using STARCCM+, reducing solver time from 115 hours to 23 hours with a maximum temperature deviation of 0.8°C.
        \item Analyzed and redesigned trunk size in ANSA to assess energy consumption impacts.
        \item Developed 2D/3D heat transfer models to study electronic component heating under snow coverage, improving reliability under cold conditions.
\end{tightemize}
\sectionsep

\runsubsection{WARSAK Hydel Power Station}
\descript{| Mechanical Intern }
\location{Nov 2019 - Aug 2021 | Warsak, KPK, Pakistan}
\begin{tightemize}
    \justifying
    \item Contributed to the overhaul of Unit 4 Francis Turbine at Warsak Hydel by preparing SOPs, reports, and ensuring safety tags compliance, completing the maintenance 1.5 months ahead of schedule.
\end{tightemize}
\sectionsep

\runsubsection{Pakistan Aeronautical Complex}
\descript{| Mechanical Intern }
\location{JUL 2018 – AUG 2018 | Kamra, Punjab, Pakistan}
\begin{tightemize}
    \justifying
    \item Conducted CAD design modifications and CFD analysis of the intake system for fighter aircraft using ANSYS FLUENT to improve pressure losses and engine performance.
\end{tightemize}
\sectionsep

\runsubsection{Heavy Mechanical Complex}
\descript{| Mechanical Design Intern }
\location{JUN 2018 – JUL 2018 | Taxilla, Punjab, Pakistan}
\begin{tightemize}
    \justifying
    \item Created assembly drawings, part specifications, and BOMs in SolidWorks, and conducted CFD analysis for temperature, pressure, and velocity distribution in a shell and tube heat exchanger.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Technical Skills}
%\location{Proficient with}
%PTC CREO \textbullet{} STARCCM+ \textbullet{} ANSYS FLUENT \textbullet{} SOLIDWORKS \\
%MATLAB \textbullet{} MSOFFICE (WORD,PPT,EXCEL) \textbullet{} ANSA \\
%\location{Familiar with:}
%C++ \textbullet{} Python \textbullet{} Java \textbullet{}Latex \textbullet{} CATIA  \textbullet{} Arduino
%\sectionsep

\section{Skills}
\begin{tabular}{rlll}
\textbf{SKILL} & \textbf{PROFICIENT} & \textbf{GOOD KNOWLEDGE}   & \textbf{FAMILIAR}  \\

\textbf{PROGRAMMING}& MATLAB & PYTHON & C++ \textbullet{} JAVA\textbullet{} \LaTeX \\
\textbf{CAD} & PTC CREO & SOLIDWORKS \textbullet{} ANSA & CATIA V5 \textbullet{} SOLIDEDGE \textbullet{} AUTOCAD \\
\textbf{CFD} & STARCCM+ & ANSYS FLUENT  & TEAMCENTER\\
\textbf{OTHER} & MS OFFICE SUITE & ADOBE PREMIERE\textbullet{} LIGHTROOM  & ARDUINO \textbullet{} LINUX \textbullet{} WINDOWS\\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}
\justifying
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\subsection{\href{https://web.uniroma1.it/cdaingtrasporti/}{Sapienza University Rome}}
\descript{MSc Transport System Engg}
\location{Sept 2021 - Mar 2024 | ITALY}
\cvtag{\textbf{Master Thesis:} Optimisation of Road Runoff Prediction Tools}\\
\location{Final Grade : {\footnotesize \textit{\textbf{96 / 110 \textbullet{} 87\% marks }}}}

\sectionsep

\subsection{\href{https://www.mech.kuleuven.be/en}{KU Leuven}}
\descript{Engineering Science}
\location{Feb 2022 - Feb 2023 | BELGIUM}
\sectionsep

\subsection{UET Peshawar}
\descript{B.Sc. in Mechanical Engg}
\location{Sept 2015 - Sept 2019 | PAKISTAN}
\location{Final Grade : {\footnotesize \textit{\textbf{3.4 / 4.0 GPA \textbullet{} 85\% marks}}}}
\location{Top 10\% of students}
\cvtag{\textbf{Bachelor Thesis:} Fuel Theft Prediction System {\footnotesize \textit{\textbf{(3rd/43 Exhibited Projects) }}}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\subsection{Graduate}
Programming for Transport System \textbullet{} Advanced Mechanical Design \textbullet{} Computational Thermo-fluids Analysis \textbullet{} Virtual Product Development \textbullet{} Artificial Neural Networks \& Deep Learning \textbullet{} Transport Modelling \textbullet{} Railway Engg \textbullet{} Traffic \& ITS \textbullet{} Safety for Industrial Aspects
\sectionsep

\subsection{Undergraduate}
Machine Design \textbullet{} Engg Mechanics \textbullet{} Engineering Drawing \textbullet{} Computer Aided Design (CAD) \textbullet{} Heat \& Mass Transfer \textbullet{} Fluid Mechanics \textbullet{} Material Science \textbullet{} Thermodynamics \textbullet{} Powerplants \textbullet{} Automatic Control \textbullet{} Engg Dynamics \textbullet{} Mechatronics \textbullet{} Metallurgy 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{LANGUAGE SKILLS}
\begin{tabular}{lllll}
\textbf{LANGUAGE} & \textbf{CEFR}   & \textbf{ORGANISATION}  \\
 
ENGLISH & C1 & IELTS \\

DUTCH	& A2 & CLT KULEUVEN \\

ITALIAN & A2 &  

\end{tabular}
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links}
%Github:// \href{https://github.com/}{\bf HOSSAINA007} \\
%LinkedIn://  \href{https://www.linkedin.com/in/hossaina007/}{\bf HOSSAINA007}
%\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     NEW PAGE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage % Move to the second page

% Second Page Layout
\begin{minipage}[t]{0.63\textwidth}


\section{TECHNICAL PROJECTS}
\runsubsection{\href{https://github.com/HossainA007/Cabin-Heatup-3D-Simulations}{\textbf{CABINHEATUP OPTIMISATION} \faExternalLink}}
\descript{| STARCCM+, ANSA, JAVA | 2024}
\descript{SUPERVISOR: DR RANDI FRANZKE / EMIL WILESON}
\vspace{0.9em}
\begin{tightemize}
   \justifying
    \item \textbf{Phase 1:} Validated wind tunnel data against simulations to ensure accurate temperature readings.
    \item \textbf{Phase 2:} Developed optimized parameters (timestep, iterations) for improved solver efficiency in transient and steady-state simulations.
    \item \textbf{Phase 3:} Accelerated convergence by freezing flow during transient phases and increasing timesteps.
    \item \textbf{Phase 4:} Automated batch simulation runs using Java macros.
\end{tightemize}
\sectionsep

\runsubsection{FUEL THEFT PREDICTION SYSTEM}
\descript{| OBD, PYTHON | 2019}
\descript{SUPERVISOR: DR MUHAMMAD ALAM ZAIB KHAN}
\begin{tightemize}
\justifying
\item Designed a fuel theft prediction system as part of B.Sc. thesis, to monitor fuel consumption in university vehicles.
    \item \textbf{Phase 1:} Collected sensor data from the ECU using an OBD tool (ELM 327).
    \item \textbf{Phase 2:} Transferred data to a web server via the Torque Pro application.
    \item \textbf{Phase 3:} Analyzed data to define three fuel theft conditions.
    \item \textbf{Phase 4:} Tested and validated results; implemented notifications for the vehicle owner in case of fuel theft detection.
\end{tightemize}
\sectionsep

\runsubsection{TRAFFIC CONGESTION ESTIMATION}
\descript{| MATLAB | 2022}
\descript{SUPERVISOR: DR CHIARA COLUMBARONI}
\begin{tightemize}
\justifying
     \item Developed a real-time traffic congestion estimation system using MATLAB for urban roads.
    \item Implemented K-Means Clustering Algorithm to assess congestion levels across different roads.
    \item Applied Dijkstra’s Algorithm to determine the shortest congestion-free route from the driver’s location to their destination.
\end{tightemize}
\sectionsep

\runsubsection{WATER DESALINATION SYSTEM}
\descript{| ANSYS/ SOLIDWORKS | 2018}
\descript{SUPERVISOR: DR ALI KAMRAN}
\begin{tightemize}
\justifying
    \item Designed a parabolic trough and solar still desalination system to produce drinkable water for the region of Gwadar.
    \item Achieved 12 liters of purified water per 8-hour operating cycle with a net efficiency of 68%.
    \item Laboratory testing showed 97\% removal of contaminants from initial saline water samples.
    \item Project results were published in IEEE Xplore.
\end{tightemize}
\sectionsep

\section{AWARDS}
\begin{tabular}{rll}
\textbf{YEAR}     & \textbf{DESCRIPTION} & \textbf{ORGANISATION}\\
2023	     & IAESTE TRAINEESHIP   & \textcolor{awesome-red}{VOLVO CARS SWEDEN}\\
2020	     & M.Sc. SCHOLARSHIP  & \textcolor{awesome-red}{ITALIAN GOVT (LAZIODISCO SCHOLARSHIP)}\\
2019	     & 3\textsuperscript{th}/43  & \textcolor{awesome-red}{BSc FINAL YEAR PROJECT EXHIBITION}\\
2015     & 229\textsuperscript{th}/13000 & \textcolor{awesome-red}{UNIVERSITY ENTRANCE EXAMINATION}  \\
2015     & B.Sc. SCHOLARSHIP & \textcolor{awesome-red}{KPK BENEVOLENT FUND} \\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Add skills entries here
\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CERTIFICATIONS}

\subsection{At VOLVO CARS BY SIEMENS}
STARCCM+ Fundamentals\\
STARCCM+ Heat Transfer Simulations\\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     GRANTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EU ERASMUS+ GRANTS}

\textbf{\texteuro300 } Exchange ,Zakopane,Poland \\
\textbf{\texteuro7000} Exchange,Leuven,Belgium \\
\textbf{\texteuro320 } Exchange,Panezevys,Lithuania \\
\textbf{\texteuro285 } Exchange,Sibiu,Romania\\
% Add certifications entries here

\section{Publications} 
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage}

\end{document}
 

